---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# xisoband

<!-- badges: start -->
[![R-CMD-check](https://github.com/hypertidy/xisoband/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/hypertidy/xisoband/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of xisoband is to make isoband a bit more generally useable. 


## Example

This example shows how to get the output of isoband as a *list of lists* of matrices, and to simply plot it. 

We avoid

- creating redundant rectilinear vectors of `$x` and `$y`
- requirement to specify levels (we auto them)
- having to convert from iso type to sf to finish the job

```{r example}
library(xisoband)
e <- whatarelief::elevation()
plot(iso <- xisoband::xisobands(e, extent = c(-180, 180, -90, 90)))
maps::map(add = TRUE, col = "firebrick", fill = FALSE)

ximage::ximage(e, extent = c(-180, 180, -90, 90))
plot(iso, add = TRUE)
```

We are using the hypertidy raster reader `elevation()` to get GEBCO 2021 elevation in a matrix, and ximage to plot it. The 'hypertidy way' is to specify `extent` directly when it is required, not a mix of xmin,xmax or xlim,ylim, or the degenerate rectlinear model used by `image()`. 

The orientation is *raster-order*, which is used by the GDAL packages and `rasterImage()`. There is a plot method for `isoband,iso` objects. 

We otherwise would get an unuseable list of grouped `x,y,id` lists from `isoband::isobands()`, or a list of `sfg` geometries (matrices in a list with a class for sf) with `iso_to_sfg()` that further processes the `isobands()` output . 

The plot method uses `graphics::lines()` currently, but could use the vectorized grid package plotting. It seems funny that isoband currently returns an output that requires further clean up, *and* converts to sf. 

If `extent` is not provided we treat the matrix as living in `0:ncol,0:nrow` space. 

We might contribute changes to isoband to clean this up, but first I needed to be able to explore what's already there. 

A rough set of goals: 

- [ ] add vectorized `grid` package plotting
- [ ] separate the raw `isobands()` output from the cleaned up version (in the same format)
- [ ] separate the conversion to sf
- [ ] put the geometry clean up deeper in the code, why do we want the raw `isobands()` output?, for example
- [ ] record the grid attirbutes (dimension and extent) on the output
- [ ] record the auto generated hi/lo levels

A simpler example, this shows the simplicity of not requiring even extent as input, we simply assume the data lives in grid space, and we have a convenient way to choose just one level (or none, but choosing here gives a good result). 

```{r simple}
m <- diag(5)
(x <- xisobands(m, lo = .5))
ximage::ximage(m)
plot(x, add = TRUE)
```

## Code of Conduct
  
Please note that the xisoband project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
